\documentclass[../thesis.tex]{subfiles}

\begin{document}

\section*{Acknowledgments\label{sec:ack}}
\addcontentsline{toc}{section}{Acknowledgments}

I would like to express my sincerest gratitude to my patient and supportive supervisor Professor( Dr.\ hab.\ ?)Bogdan Rosa for his strong motivation and excellent supervision during several years of my Ph.D.\ studies. I do appreciate his immense knowledge and invaluable experience that continuously inspired me in my academic research as well as daily life. I am also truly thankful to both Professor Dr.\ hab.\ Jacek Pozorski (\href{https://www.imp.gda.pl/en/}{Institute of Fluid-Flow Machinery}, Polish Academy of Sciences, Poland) and Professor Lian-Ping Wang (\href{https://www.sustech.edu.cn/en/}{Southern University of Science and Technology}, China) for helping us in a \href{https://doi.org/10.1017/jfm.2021.229}{collaborative study} by providing critical inputs and valuable feedback to obtain and analyze the results. A special thanks to my friend and colleague \mbox{Dr.\ Antoine Michel} who is always willing to share ideas and offer assistance. I would also like to thank the committee members for
% taking time to read, review, and for your brilliant comments and suggestions.
(Furthermore, I would like to acknowledge all creators, maintainers, and developers of the pseudo-spectral solver code, especially Prof. Lian-Ping Wang (University of Delaware; currently Southern University of Science and Technology, Shenzhen) and Dr. hab. Bogdan Rosa, as well as the copyright holder, University of Delaware, for permission to use and modify it in order to obtain results presented in this thesis?)
My family deserves endless gratitude for all the love and support they have given to me that keeps me motivated. 

This thesis has been created in the framework of the \href{https://projekty.ncn.gov.pl/en/index.php?projekt_id=417540}{project} ``\emph{Numerical modeling of dispersed turbulent flows considering particle-scale interactions},'' funded by the (i) \textsl{National Science Center} (\href{https://www.ncn.gov.pl/en}{NCN}) of Poland under the grant \mbox{2018/30/Q/ST8/00341}. Computational resources have been provided by both the (ii) \textsl{Interdisciplinary Center for Mathematical and Computational Modeling} at the University of Warsaw (\href{https://icm.edu.pl/en/}{ICM--UW}), Poland, under grants \mbox{GA73-14}, \mbox{GA84-22}, \mbox{G87-1145}, and \mbox{G92-1450}, as well as the (iii) \textsl{Institute of Meteorology and Water Management -- National Research Institute} (\href{https://www.imgw.pl/}{IMGW--PIB}). I would like to gratefully acknowledge the support we received from all these institutions.

\newpage
\end{document}
